\chapter{Conclusion}
\label{ch5:conclusion}

This thesis has demonstrated methods to modeling and optimization using \gls{GP}. It
is motivated by the need to reduce the activation energy required to use
optimization for conceptual design. The \gls{GP} and \gls{SP} are the
mathematical frameworks that enable the intuitive formulation of general
physical relations into optimization-compatible constraints.

In Chapter~\ref{ch2:inequalities}, the ideas of pressure and boundedness were
defined in the context of a \gls{GP}. The basic aircraft design problem was defined,
and the importance of objective functions and variable freedom
was identified in achieving bounded convex problems.
Section~\ref{s:GPlimits} provided justification for the need to use the non-convex
extension of \gls{GP}s called \gls{SP}s in design, with some loss of mathematical
guarantees and solution speed. Fuel volume models provided a meaningful use
case for signomial constraints, and the chapter provided arguments for the use of the signomial
equality. The result was a fully bounded \gls{SP}-compatible aircraft model that captures
fundamental tradeoffs in conceptual aircraft design.

Chapter~\ref{ch3:extensibility} introduced the idea of modularity, and improved
the fidelity of the aircraft model by using data-based modeling in Section~\ref{s:engine}.
The model was subsequently modularized
into component models, and then into performance and static models in order to
be able to vectorize certain sets of variables and constraints that are repeated between
different mission segments. A logical (but non-unique) hierarchy of models
was presented to allow designers to make decisions about where to locate different variables
and constraints in the modular mission architecture.

Chapter~\ref{ch3:extensibility} also presented a case where environmental modeling becomes critical
for designs we trust as engineers. While performing tradespace exploration, an intuitive
way to analyze the components of a multi-objective \gls{GP} was presented, in
an effort to draw maximal engineering understanding from the tradespaces that were explored.

Before the model was integrated into a multimission framework in Section~\ref{s:multimission},
the SimPleAC engine model was improved upon
in response to the sensitivity information. Potential
new objective functions were identified and implemented in the context of multimission design
and optimization.
A sample solution of a 2-mission multimission aircraft design
was presented alongside two aircraft optimized for each mission alone to further motivate
the use of multimission \gls{MDO}.

This thesis has demonstrated how to model a complex engineering system
starting from scratch in \gls{GP} and \gls{SP} using
using component and function based abstractions. Using tools developed in the \gls{CEG},
it has outlined methods that allow designers to extract engineering understanding of
the trade spaces using convex and difference-of-convex methods.
Although an aircraft design problem was the focus of the thesis,
these methods are general to engineering design problems with explicit, continuous constraints,
and lower the barriers to using optimization in engineering design.

