% -*-latex-*-
% 
% For questions, comments, concerns or complaints:
% thesis@mit.edu
% 
%
% $Log: cover.tex,v $
% Revision 1.8  2008/05/13 15:02:15  jdreed
% Degree month is June, not May.  Added note about prevdegrees.
% Arthur Smith's title updated
%
% Revision 1.7  2001/02/08 18:53:16  boojum
% changed some \newpages to \cleardoublepages
%
% Revision 1.6  1999/10/21 14:49:31  boojum
% changed comment referring to documentstyle
%
% Revision 1.5  1999/10/21 14:39:04  boojum
% *** empty log message ***
%
% Revision 1.4  1997/04/18  17:54:10  othomas
% added page numbers on abstract and cover, and made 1 abstract
% page the default rather than 2.  (anne hunter tells me this
% is the new institute standard.)
%
% Revision 1.4  1997/04/18  17:54:10  othomas
% added page numbers on abstract and cover, and made 1 abstract
% page the default rather than 2.  (anne hunter tells me this
% is the new institute standard.)
%
% Revision 1.3  93/05/17  17:06:29  starflt
% Added acknowledgements section (suggested by tompalka)
% 
% Revision 1.2  92/04/22  13:13:13  epeisach
% Fixes for 1991 course 6 requirements
% Phrase "and to grant others the right to do so" has been added to 
% permission clause
% Second copy of abstract is not counted as separate pages so numbering works
% out
% 
% Revision 1.1  92/04/22  13:08:20  epeisach

% NOTE:
% These templates make an effort to conform to the MIT Thesis specifications,
% however the specifications can change.  We recommend that you verify the
% layout of your title page with your thesis advisor and/or the MIT 
% Libraries before printing your final copy.
\title{Conceptual Engineering Design and Optimization Methodologies using Geometric Programming}


\author{Berk \"Ozt\"urk}
% If you wish to list your previous degrees on the cover page, use the 
% previous degrees command:
%       \prevdegrees{A.A., Harvard University (1985)}
% You can use the \\ command to list multiple previous degrees
%       \prevdegrees{B.S., University of California (1978) \\
%                    S.M., Massachusetts Institute of Technology (1981)}
\prevdegrees{B.S., Massachusetts Institute of Technology, 2016}
\department{Department of Aeronautics and Astronautics}

% If the thesis is for two degrees simultaneously, list them both
% separated by \and like this:
% \degree{Doctor of Philosophy \and Master of Science}
\degree{Master of Science in Aeronautics and Astronautics}

% As of the 2007-08 academic year, valid degree months are September, 
% February, or June.  The default is June.
\degreemonth{February}
\degreeyear{2018}
\thesisdate{February 1st, 2018}

%% By default, the thesis will be copyrighted to MIT.  If you need to copyright
%% the thesis to yourself, just specify the `vi' documentclass option.  If for
%% some reason you want to exactly specify the copyright notice text, you can
%% use the \copyrightnoticetext command.  
%\copyrightnoticetext{\copyright IBM, 1990.  Do not open till Xmas.}

% If there is more than one supervisor, use the \supervisor command
% once for each.
\supervisor{Mark Drela}{Professor, Aeronautics and Astronautics}

% This is the department committee chairman, not the thesis committee
% chairman.  You should replace this with your Department's Committee
% Chairman.
\chairman{Hamsa Balakrishnan}{Associate Professor, Aeronautics and Astronautics\\
Chair, Graduate Program Committee}

% Make the titlepage based on the above information.  If you need
% something special and can't use the standard form, you can specify
% the exact text of the titlepage yourself.  Put it in a titlepage
% environment and leave blank lines where you want vertical space.
% The spaces will be adjusted to fill the entire page.  The dotted
% lines for the signatures are made with the \signature command.
\maketitle

% The abstractpage environment sets up everything on the page except
% the text itself.  The title and other header material are put at the
% top of the page, and the supervisors are listed at the bottom.  A
% new page is begun both before and after.  Of course, an abstract may
% be more than one page itself.  If you need more control over the
% format of the page, you can use the abstract environment, which puts
% the word "Abstract" at the beginning and single spaces its text.

%% You can either \input (*not* \include) your abstract file, or you can put
%% the text of the abstract directly between the \begin{abstractpage} and
%% \end{abstractpage} commands.

% First copy: start a new page, and save the page number.
\cleardoublepage
% Uncomment the next line if you do NOT want a page number on your
% abstract and acknowledgments pages.
% \pagestyle{empty}
\setcounter{savepage}{\thepage}
\begin{abstractpage}
\input{abstract}
\end{abstractpage}

% Additional copy: start a new page, and reset the page number.  This way,
% the second copy of the abstract is not counted as separate pages.
% Uncomment the next 6 lines if you need two copies of the abstract
% page.
% \setcounter{page}{\thesavepage}
% \begin{abstractpage}
% \input{abstract}
% \end{abstractpage}

\cleardoublepage

\section*{Acknowledgments}

Firstly, I would like to thank Professor Warren Hoburg for giving me
the opportunity to work on research that I believe has great potential.
He introduced me to geometric programming and welcomed me to the Hoburg Research Group
(now the Convex Engineering Group). Under his mentorship, I learned that the most interesting designs
are the ones we don't expect, and that challenging current engineering design methods and norms
is the most worthwhile objective of optimization.
So thank you for the opportunity to do just that.

I am grateful for the many friends I have in the Aerospace Computational Design
Lab (ACDL) who have lightened my work hours with their camaraderie. Of this group,
the Convex folks reserve a special place. I am lucky to collaborate with
such a talented and dedicated group of researchers, and I hope that we will continue
to redefine conceptual engineering design.

This thesis would not have been possible without the amazing work Ned Burnell does
as the lead developer of GPkit. He never ceases to amaze me with his creativity and energy.
The many debates we have had about design philosophy have inspired this thesis,
and I'm glad I've gotten the opportunity to extensively document many of the ideas
that were discussed.

I thank my co-advisors Professor Mark Drela and Bob Haimes, who have taken on the burden of advising
me in Woody's absence. Thank you for your guidance and wisdom, and pushing me to
finish this thesis.

I am indebted to cycling for keeping me fit and sane. Cycling has given me opportunities to
escape, even as I miss winter training camp to conclude this thesis.
MIT Cyclists have been an immutable source of joy in my life, and are near and dear
to my heart. Thanks for enabling me.

I would like to thank my long-time friend Johannes Norheim
for being a battle-scarred companion through 5 years of MIT. We have been challenged, and
our paths have converged and diverged many times, but our friendship has not wavered.
My partner Elise Newman has been a ray of sunshine in every weather,
and I am looking forward to our future adventures together.

My parents definitely deserve a mention because I wouldn't exist without them.
The longer I live, the more I understand that I am where I am because of the
sacrifices they have made.
Deniz, you have been my rock. It has been my privilege to be your brother and watch
you grow up, and will be my privilege to help you
through your struggles and celebrate your future successes.
I am confident you will be more than I have been.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% -*-latex-*-
