\chapter{Introduction}

Modern engineering design, and particularly aerospace design, has come to rely
heavily on optimization. Time and time again, the importance of fast and
reliable MDO tools has been stressed in the literature. However most MDO tools
have the downfalls of being slow due to the multimodal nature of many
engineering design problems.
	
In the \gls{CEG}, we seek to improve the engineering design process by
leveraging the mathematical guarantees of convex optimization, and developing
open-source, object-oriented software to help build GP-compatible models and
interface with solvers. In much of our previous work
(\cite{gp_ac_design},\cite{SP_ac_design}, \cite{turbofan}), we have demonstrated that
\gls{GP} is useful for optimization, but have yet to formalize why it
facilitates design.
 
The mathematical restrictions on the form of constraints remains the biggest
barrier in the implementation of convex programs in design. Firstly, this thesis
will aim to show that the form of the GP actually facilitates the design process
and engineering understanding, rather than impeding it. Hence it will aim to
pass on some of the expertise we have developed in the \gls{CEG} building
\gls{GP}-compatible models.

Secondly, it will aim to showcase the features of GPkit in further facilitating
an engineering design process that is streamlined and collaborative, and is
compatible with modern engineering design methodologies (flexibility and
modularity). GPkit allows feedback between design engineers and models (speed
and sensitivities) which allows targeted efforts by engineers to improve models.

(NED Comment: What about conceptual design? Collaboration?)

\section{Defining Design versus Optimization} \label{sec:DesVsOpt}

\subsection{What is design?}

\begin{itemize}
\item To conceive the look (the form) and function of something. 
\item Ned's comment: Parametrization and physics. Hard to agree on a representation that we all agree on. 
\item It is a PROCESS
\begin{itemize}
	\item The 'look' is the configuration
	\item The function is oftentimes what we can quantify
\end{itemize}
\item Essentially a class of feasibility problems, given a set of requirements. 
\end{itemize}

\subsection{What is optimization?}

\begin{itemize}
\item Has a rigorous mathematical definition: The selection of an element in a set 
of feasible solutions with the lowest desired objective function value. 
\item It is also a process!
\item It is sensitive to the choice of objective function, and the elements 
contained within the set (configuration)
\item To many engineers, design and optimization are one and the same. 
\end{itemize}

\subsection{What are the fundamental differences?}

\begin{itemize}
\item Design is human-driven. Optimization is computational. 
\item Design is based on feasibility. Optimization is based on the mathematical guarantees of optimality. 
\item Design can be done in non-restrictive mathematical forms. Optimization is done in specific mathematical forms that take advantage of structure. 
\end{itemize}

\section{Unifying design and optimization using gls{GP}}


\gls{GP} has developed "in response to a need to solve problems in the actual 
world".~\cite{duffingp} Quote from Duffin, 1967, main inventor of GP.

(Each section in this part of the intro has a corresponding section in the body.
(Each will feature an example problem that I will run through as a
(demonstration.)

There are three primary reasons why...

\begin{enumerate}     \item \textit{Inequalities help engineering
understanding.}

The mathematical constraints of \gls{GP} force designers to have a proper grasp
of the fundamental tradeoffs and pressures in a design.

Inequalities make feasible sets explicit. ADD A DIAGRAM OF FEASIBLE SETS using
SimPleAC HERE.

Traditionally, physical relations are expressed as equalities. But there is an
almost-seamless transition from fundamental physics to GP-compatible
constraints. ENGINEERS LIKE +VE QUANTITIES. eg. downforce vs. negative lift.

And even if the tradeoffs are not clear, we can use signomial equalities to
enforce constraints.

    \item \textit{Models are extensible.}
    
Models can be made arbitrarily complex. The 'bag of constraints' form of the GP
means that there is no need to reformulate the optimization scheme as more
constraints are added. This makes incremental modeling improvements possible and
even preferable.

The traditional engineering design process is split into conceptual, preliminary
and critical design segments. GP modeling facilitates this process by allowing
ever-increasing levels of complexity.

Gradient based optimization methods for multimodal systems often involves
converge loops, which have to be reengineered when new constraints are
introduced. VS. adding constraints to a bag...

We can effectively use sensitivity information to determine which parts of the
model yield the greatest returns to improved modeling, so engineers can target
their efforts.

    \item \textit{Models are flexible and modular, and compatible with modern
    engineering design (similar to extensible?)}

(This is a feature of GPkit, and not GPs in general.) \gls{GP}s make it easy to
implement component-based modeling, and build models that are shared between
different design problems. Each component has associated sizing and performance
variables.

This is helped by the fact that underconstrained \gls{GP}s can solve reliably,
and the tightness of constraints can be monitored.

\end{enumerate}



